%%
%% This is file `cvtest.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% currvita.dtx  (with options: `testfile')
%% 
%% LaTeX sample file for the currvita package
%% 
%% Copyright (C) 1999 Axel Reichert
%% See the files README and COPYING.
%% 
%% \CharacterTable
%%   {Upper-case    \A\B\C\D\E\F\G\H\I\J\K\L\M\N\O\P\Q\R\S\T\U\V\W\X\Y\Z
%%   Lower-case    \a\b\c\d\e\f\g\h\i\j\k\l\m\n\o\p\q\r\s\t\u\v\w\x\y\z
%%   Digits        \0\1\2\3\4\5\6\7\8\9
%%   Exclamation   \!     Double quote  \"     Hash (number) \#
%%   Dollar        \$     Percent       \%     Ampersand     \&
%%   Acute accent  \'     Left paren    \(     Right paren   \)
%%   Asterisk      \*     Plus          \+     Comma         \,
%%   Minus         \-     Point         \.     Solidus       \/
%%   Colon         \:     Semicolon     \;     Less than     \<
%%   Equals        \=     Greater than  \>     Question mark \?
%%   Commercial at \@     Left bracket  \[     Backslash     \\
%%   Right bracket \]     Circumflex    \^     Underscore    \_
%%   Grave accent  \`     Left brace    \{     Vertical bar  \|
%%   Right brace   \}     Tilde         \~}
\documentclass[11pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage{currvita}
\usepackage[a4paper,top=2cm,left=2cm,right=2cm,bottom=2cm]{geometry}
\usepackage[utf8]{inputenc}

\newcommand*{\ac}[1]{\mbox{#1}}

\AtBeginDocument{%
    \settowidth{\cvlabelwidth}{Jan 8888 -- Feb 8888}%
}

\usepackage[colorlinks,plainpages=false,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue]{hyperref}
\def\pdfBorderAttrs{/Border [0 0 0] } % No border around Links

\begin{document}

\begin{center}
    \Huge
    \textbf{Andreea Lucau}
    \vspace{1em}
\end{center}

\begin{cv}{}
    \begin{cvlist}{Personal Information}
    \item[Date of Birth]	25 July 1986
    \item[Nationality]	Romanian
    \item[Address]
        62, The Links, Elmpark, \\
        Dublin 4, Dublin\\
        Ireland
    \item[Tel.]	+353 860 421 760
    \item[Email]		andreea.lucau@gmail.com
    \end{cvlist}

    \begin{cvlist}{Work Experience}
    \item[April 2013 -- present]
        \textbf{Software Engineer} at Amazon Data Services Ireland.

        I worked in the Network System Engineers team on projects that aim to automate various parts of the network. I work in Python.

    \item[March 2010 -- March 2013]
        \textbf{Senior Software Engineer} at IXIA Romania. (\href{http://www.ixiacom.com/}{www.ixiacom.com})

        I worked with layer 2-3 protocols implementations on a custom Linux platform used for simulating real-life networks. The purpose was to test high power routers and switches. I’ve worked on:
        \begin{enumerate}
            \item fixing bugs for DHCP(both client and server, IPv4 and IPv6) and add multithread support for DHCP
            \item developping a IGMP client
            \item implementing DCBX 802.1 Qaz standard
            \item adding multihread support for FCoE client
            \item designing a VEPA emulation and developping the code for the VDP protocol
            \item migrating the FCoE forwarder emulation to a native fiber chanel encapsulation
        \end{enumerate}
        I was responsible with scoping and writing functional specifications for my projects, taking into account customer’s need. I’ve worked with the following architectures: Power PC, Intel i686, Intel x86-64, Octeon.

    \item[July 2009 -- Feb 2010]
        \textbf{C Software Engineer} at Jinny Software (\href{http://www.jinnysoftware.com/}{www.jinnysoftware.com})

        I’ve worked on the server side of a web application destined to register and configure mobile advertising campaigns. Amongs my tasks were:
        \begin{enumerate}
            \item developing a task scheduling engine for processing database records
            \item implementing database procedures
            \item ensuring scalability and accuracy
        \end{enumerate}
        I’ve worked with C, MySql and Apache.

    \item[July 2007 -- Sep 2009]
        \textbf{C Software Engineer} at EvoSoftware

        I’ve worked on image processing algorithms for scanned documents. I’ve developed algorithms for barcode detection, line removal and color recognition.
        I've worked with C++ and C\#.
    \end{cvlist}

    \pagebreak

    \begin{cvlist}{Personal Projects}
    \item[GitHub]
        I’ve developed a small PGP encryption client, that was supposed to compress a file, search for public keys on a PGP server, download the key and use it to encrypt the file. I’ve used gnupg, gpgme, libz, curl.
        I’ve added management capabilities for the open-source VPN solution OpenVPN for my graduation project.
        Here is my GitHub page: \href{https://github.com/andreea-lucau?tab=repositories}{GitHub}.
    \end{cvlist}

    \begin{cvlist}{Prizes, Awards, Certificates}
    \item[2008]
        Cisco \textbf{CCNA} for module 1.

    \item[2004]
        3$^{th}$ place at National Physics Contest ”Stefan Procopiu” Constanta

    \item[2002]
        3$^{th}$ place at National Physics Contest ”Stefan Procopiu” Constanta
    \end{cvlist}

    \begin{cvlist}{Education}
    \item[Sep 2005 – June 2009]
        \textbf{``Politehnica" University of Bucharest}, Bucharest, Romania\\
        Automation and Computer Science, Computer Science Dept.

        I took the Systems Programming specialization in the 4th year. My graduation thesis added an auto-configuration and network management capabilities to a open-source VPN solution: OpenVPN.

    \item[Sep 2001 – Jun 2005]
        \textbf{``Dragos Voda'' National College}, Campulung Moldovenesc - Informatics Class
    \end{cvlist}

    \begin{cvlist}{Skills}
    \item[Programming]
        C/C++ (POSIX programming, BSD sockets), Python, Bash, OOP

    \item[Networking]
        HTTP, FTP, RTP, SIP, TCP, UDP, IPv4/6, MPLS, Ethernet

    \item[Databases]
        MySQL, Oracle

    \item[Version Control]  Perforce, svn, git
    \item[Operating Systems]
        GNU/Linux (Debian, Ubuntu), Windows
    \end{cvlist}

    \begin{cvlist}{Languages}
    \item Romanian (mother tongue),  English (very good), French (medium)
    \end{cvlist}

    \cvplace{Dublin, Ireland}
    \date{May 2014}
\end{cv}
\end{document}
